WHS Machine Learning: Lessons Learned

### 2013-04-26 paper/paper.tex
Updated paper

\documentclass[12pt,a4paper]{report}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{Kevin Gao,
Matt Li,
Ashvin Nair, Saavan Patel}
\title{WHS Machine Learning: Lessons Learned}
\begin{document}

@@

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

\author{Kevin Gao, Matt Li, Ashvin Nair, Saavan Patel}
\title{WHS Machine Learning: Lessons Learned}

\begin{document}

@@

\section{Decision Trees}

Decision trees classify and predict from learned data. We applied the decision tree program to car buyers, the census, congressional voting records, and CPU performance data.

\section{Genetic Algorithms}

Genetic algorithms find parameters to optimize a given function. The hungarian algorithm - ha - is a specific algorithm to maximally select elements of a matrix. We used it in combination with a genetic algorithm to create mathteam, a program to optimize math team performance.

\section{Hidden Markov Models} 
Hidden markov model algorithms perform pattern recognition. From an extracted model, the Viterbi algorithm allows prediction of underlying states from observed states.

\section{Artificial Neural Nets}
A form of function approximation learning. The project includes a neural net for optical character recognition.
